Based on polling as of 27 October 2024, Harris expects to win on 49.2%, leads Trump by 2% in 2024 US election

### 2024-10-30 paper/paper.qmd
update cross reference

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| label: fig-support-predicted
#| fig-cap: Predicted Support Trends for Kamala Harris and Donald Trump using fitted model
# Predictions for Harris
new_data_harris <- new_data_harris |>
  mutate(
    predicted_unweighted = predict(model_harris_unweighted, newdata = new_data_harris),
    predicted_weighted = predict(model_harris_weighted, newdata = new_data_harris)
  )

@@

```
The predicted support for Kamala Harris and Donald Trump, as derived from multiple linear regression models, is displayed in the graph above. The analysis spans from August 1, 2024, to October 27, 2024, and highlights both unweighted and weighted predictions for each candidate.

>>>>

```{r}
#| echo: false
#| warning: false
#| message: false
#| eval: true
#| label: fig-support-predicted
#| fig-cap: Predicted Support Trends for Kamala Harris and Donald Trump using Fitted Linear Model
# Predictions for Harris
new_data_harris <- new_data_harris |>
  mutate(
    predicted_unweighted = predict(model_harris_unweighted, newdata = new_data_harris),
    predicted_weighted = predict(model_harris_weighted, newdata = new_data_harris)
  )

@@

```
The predicted support for Kamala Harris and Donald Trump, as derived from multiple linear regression models, is displayed in @fig-support-predicted. The analysis spans from August 1, 2024, to October 27, 2024, and highlights both unweighted and weighted predictions for each candidate.
